--- 
title: Sequencing App
output: 
  flexdashboard::flex_dashboard
runtime: shiny
orientation: rows
vertical_layout: scroll 
---

<style>                     
.navbar {
  background-color:red;
  border-color:black;
}
.navbar-brand {
color:white!important;
}

</style> 

```{r libraries, include=FALSE}
source("libs.R")

##Interested within AB 
##Interested in AB after AB 


#Michael's favorite Table libraries for Dashboarding
# DT ---- gt -- > gtextras ---- reacttable -> reactablefmtr
```





Sequencing Charts {data-navmenu="Viz Tools" data-icon="fa-diagram-project"}
===========================================================================


Inputs{.sidebar}
----------------

```{r}
checkboxGroupInput(
  
  inputId = "team",
  label="Choose Team(s)",
  choices=dat %>% 
              pull(fielding_team) %>% 
              unique(),
  selected=dat %>% 
            pull(fielding_team) %>% 
            unique()
)


renderUI(
selectInput(inputId = "pitcher",
            label="Pitcher",
            choices=dat %>% 
                    filter(fielding_team %in% input$team) %>% 
                    pull(pitcher) %>% 
                    unique() %>% 
                    sort(),
            selected="Aaron Nola",
            multiple=FALSE)
)


```



Row
------

### Pitch Table

```{r}

renderDataTable({
  
datatable(
dat %>% 
  filter(isPitch==TRUE,
         pitcher== input$pitcher) %>% 
  mutate(bs_count=paste0(count.balls.start,"-",count.strikes.start),
         inplay=ifelse(details.isInPlay==TRUE,1,0),
         ptype=details.type.description,
         outs=count.outs.start
         ) %>% 
  select(pitcher,pitchNumber,bs_count,outs,ptype,inplay,details.description),
extensions = 'Buttons', options = list(
    pageLength = 100000, scrollY = "600px",scrollX=TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
        
  ),rownames=FALSE
)

})
```






### Strikezone Plot

```{r}
topKzone = 3.5
botKzone = 1.5
inKzone = -.85
outKzone = 0.85

kZone = data.frame(
  PlateLocSide = c(inKzone, inKzone, outKzone, outKzone, inKzone)
  , PlateLocHeight = c(botKzone, topKzone, topKzone, botKzone, botKzone)
)

 
renderPlotly({
 
ggplotly(
  ggplot()+
  geom_point(data=dat %>% 
               mutate(ptype=details.type.description) %>% 
  filter(pitcher==input$pitcher,
         is.na(ptype)==FALSE),
  aes(x=pitchData.coordinates.pX,y=pitchData.coordinates.pZ,color=ptype,label=details.description))+geom_label()+coord_equal()+
    geom_path(aes(PlateLocSide,PlateLocHeight),data=kZone)+
       geom_segment(aes(x=-8.5/12,xend=8.5/12,y=(10/12)-1,yend=(10/12)-1),color="white")+ggtitle("Pitch Locations")+xlab("Location X (ft)")+ylab("Location Z (ft)")+
    geom_segment(aes(x=-8.5/12,xend=-8.5/12,y=(10/12)-1,yend=0),color="white")+
    geom_segment(aes(x=8.5/12,xend=8.5/12,y=(10/12)-1,yend=0),color="white")+
    geom_segment(aes(x=8.5/12,xend=0,y=0,yend=(15/12)-1),color="white")+
    geom_segment(aes(x=-8.5/12,xend=0,y=0,yend=(15/12)-1),color="white")+
     dark_theme_bw()
)

})
```


Row 
-------


### Model Output

```{r}

```


### Other

```{r}

```






Summary Tables {data-navmenu="Viz Tools" data-icon="fa-user"}
====================================================================

Inputs{.sidebar}
----------------

```{r}
### Scrape Savant data from a particular day --- i've select a day for you -- use this data frame throughout this page
savant_data <- baseballr::scrape_statcast_savant_pitcher_all(start_date="2021-04-05",
                                              end_date="2021-04-05")

 

## in this same chunk create a selection dropdown for pitcher names , which is player_name use selectInput
```


Row
-----

### 

```{r}
#present pitch characteristics in this section, such as release speed, break characteristics, etc. -- make sure the table is dynamic, referencing the selectInput id for the pitcher that the user selects
```

###

```{r}
#create a reactive plot of your choosing here that shows release points for from a side view and from behind the pitcher ---
```




Row
-----

###

```{r}

```


###

```{r}

```



Ad-Hoc Visuals {data-navmenu="Viz Tools" data-icon="fa-user"}
====================================================================


Inputs{.sidebar}
-------------------

```{r}

```


Row
-----------

###

```{r}

```


###

```{r}

```

Row
-----------

###

```{r}

```


###

```{r}

```







Model Validation {data-navmenu="Interactive Modeling" data-icon="fa-user"}
====================================================================

Inputs{.sidebar}
----------------

```{r}
### Scrape Savant data from a particular day --- i've select a day for you -- use this data frame throughout this page
savant_data <- baseballr::scrape_statcast_savant_pitcher_all(start_date="2021-04-05",
                                              end_date="2021-04-05")

 

## in this same chunk create a selection dropdown for pitcher names , which is player_name use selectInput
```


Row
-----

### 

```{r}
#present pitch characteristics in this section, such as release speed, break characteristics, etc. -- make sure the table is dynamic, referencing the selectInput id for the pitcher that the user selects
```

###

```{r}
#create a reactive plot of your choosing here that shows release points for from a side view and from behind the pitcher ---
```




Row
-----

###

```{r}

```


###

```{r}

```



Matchup Results {data-navmenu="Interactive Modeling" data-icon="fa-user"}
====================================================================


Inputs{.sidebar}
-------------------

```{r}

```


Row
-----------

###

```{r}

```


###

```{r}

```

Row
-----------

###

```{r}

```


###

```{r}

```

Model Drag and Drop {data-navmenu="Interactive Modeling" data-icon="fa-user"}
====================================================================


Inputs{.sidebar}
-------------------

```{r}

```


Row
-----------

###

```{r}

```


###

```{r}

```

Row
-----------

###

```{r}

```


###

```{r}

```


Relief Pitcher Selection Tool {data-navmenu="Decision Tools" data-icon="fa-user"}
====================================================================

Inputs{.sidebar}
----------------

```{r}
### Scrape Savant data from a particular day --- i've select a day for you -- use this data frame throughout this page
savant_data <- baseballr::scrape_statcast_savant_pitcher_all(start_date="2021-04-05",
                                              end_date="2021-04-05")

 

## in this same chunk create a selection dropdown for pitcher names , which is player_name use selectInput
```


Row
-----

### 

```{r}
#present pitch characteristics in this section, such as release speed, break characteristics, etc. -- make sure the table is dynamic, referencing the selectInput id for the pitcher that the user selects
```

###

```{r}
#create a reactive plot of your choosing here that shows release points for from a side view and from behind the pitcher ---
```




Row
-----

###

```{r}

```


###

```{r}

```



Sequence Optimization Tool {data-navmenu="Decision Tools" data-icon="fa-user"}
====================================================================


Inputs{.sidebar}
-------------------

```{r}

```


Row
-----------

###

```{r}

```


###

```{r}

```

Row
-----------

###

```{r}

```


###

```{r}

```

